|

### 2025-05-23 Reviews/round_1/rebuttal_point_by_point.md

# Rebuttal to Reviewer Comments – Round 1

Thank you for the constructive feedback. Below is our detailed, point-by-point response to the reviewers' comments. Reviewer comments are in **bold**, and our responses follow in regular text with manuscript changes noted where applicable.

---

## Reviewer 1

> This paper investigates whether and how the integration of large language models (LLMs) into classroom activities influence students’ learning. Although the topic, questions, and results are crucial, the manuscript requires revision before publication. Therefore, I recommend a major revision, and I am willing to review the revised manuscript. I have provided a list of comments below to assist the authors in transforming their paper into a manuscript worthy of publication.

### Comments

> The abstract sound great.

Thanks!

> The literature review provides a broad context for AI’s potential; however, it lacks a strong connection to recent studies that address AI’s evolving role in educational contexts, critical thinking, and argumentative writing. The paper could enhance its theoretical foundation by engaging more deeply with contemporary research on AI’s impact on students' critical thinking, argumentation and reasoning. There are much more recent studies by scholars such as Kazem Banihashem and that you can consult with.

We did ...

> Please justify why the participants come from Brussels (Belgium) and one in Seville (Spain)? Why these two countries and these two cities? What is the argument here?

We recruited two schools in different countries to increase the external validity of our study. The country choice was by convenience as the authors lived in Brussels and Seville at the time of the experiment. We sought schools with similar curricula and contacted the schools through personal connections. The selected schools were both international with students from comparable socio-economic backgrounds, which was ideal for conducting the experiment.

> More information on the method section, the context, the design, and the participant characteristics are needed to give the readers a clear description of the study. Please elaborate on the background information of the characteristics of the participants that could influence the way learners engage with AI and critical thinking and argumentation. Acknowledging these limitations can guide future research in this area.

We have included more information ....

> The results show promising outcomes. However, the findings of this study are derived from self-reported data collected from participants through surveys. However, it is important to note that the literature suggests caution in heavily relying on such self-reported data, as perception does not always equate to actions (see: https://urldefense.com/v3/__https://doi.org/10.1080/02602938.2024.2345669__;!!DOxrgLBm!DU2xLNvI0Ke45t43rGQAI3BYa8bni0Io2JesBwINodtn8kzLHvspBE2my62mGZlAoKzFv6RFxgUv6FWyBQIbCg9ObQu4SA$ ). Therefore, this must be acknowledged as a limitation of the study, along with suggestions for future research to address this issue.

We have discussed this limitation in the conclusions ...

> The depth and width of the discussion section could be improved by incorporating relevant and recent literature. This would provide more theoretical insights and add value to the study by linking the findings to the broader literature.

Many thanks we have ...

## Reviewer 2

> The article deals with a current and pressing topic. Since AI-based Large Language Models have become freely accessible, the way in which students learn has changed rapidly. There are new opportunitiesbut also risks for didactic methods. The article addresses the use of an AI tutor to support students' learning and understanding. An experimental setup is used to investigate the conditions under which an AI tutor enhances learning, how an AI tutor influences students' confidence in their own performance, and whether an AI tutor is perceived as helpful by students.

### Comments

> The article presents three research questions. The first question should be expressed with greater precision. Of particular note, the second part of the research question is not addressed by the selected experiments. The second research question, which comprises two distinct inquiries, should be subdivided to enhance its clarity and comprehensibility. The research questions are derived from existing literature. However, this section is rather brief. Notably, no hypotheses have been formulated or derived from the literature. Only one hypothesis has been stated explicitly. However, this has been done in the results section only, contrary to scientific conventions.

Clarified the research questions.

> In the Methods section and in the Supplementary Materials, the experimental procedure is largely described in a comprehensive and reproducible manner. However, the methods/experiments/questionnaire items are not related to the previously stated research questions or hypotheses. This makes it unnecessarily difficult for the reader to assess the validity of the approach chosen to address the research questions. To enhance comprehensibility, it would be beneficial to explicitly label the independent and dependent variables, as well as the control variables collected for each research question/hypothesis.

Ok.

> The results section first describes the group of subjects. For one experimental intervention (socratic AI tutor), it is reported whether the experimental group differed significantly from the control group. However, this information is missing for the other experimental intervention (AI explanation). In the remainder of the section, the analyses of the dependent variables are presented in a largely scientific manner. Notably, for the first experimental manipulation, a dependent variable has been listed in the methods section (propensity to update initial guess). However, no results are reported for this variable, and I do not understand what was done with this data or why it wasn't used. In the second experimental manipulation (socratic tutor), variables are reported that have not been described in the methods section. These new variables that measure the interaction with the AI tutor are only (and very briefly) motivated here. They should be motivated in the Introduction and included in the Methods section.

Ok.

> Contrary to usual conventions, some results with a significance level greater than 0.1 are reported as significant. In addition, in some cases, the language used is not specific/detailed enough to correctly understand the analyses (Which analysis uses exactly which data or answers from the questionnaire?). In some cases, the methods used are only briefly named and may therefore not be reproducible (in particular bootstrap method, in some cases also regression models - which variables exactly have been included?).

> The discussion addresses the research findings and identifies some methodological limitations. Since there was little specific literature on the specific research questions in the Introduction, the discussion of the results in the context of the existing literature is also very brief. However, it is particularly striking that the entire discussion does not contain a single reference/citation. In my opinion, this would be essential for a scientific publication.

Ok.

> In my opinion, some interpretations of the results go too far. In particular, the data on learning and retention effects can only give first indications, because each type of task was completed exactly once by the students. The database is therefore too small to provide generalizable results. Nevertheless, the article contains interesting results, especially on the interaction/acceptance of a socratic AI tutor by people who had prior experience with chatGPT.

ok.

> The methodological discussion contains important points but could be more detailed. In particular, the validity of the methods used should be discussed (was the question about transferability of knowledge appropriate (sound/density)? ). Further, it is not discussed whether the setting at different schools in two different countries could have influenced the results.

OK

> Overall, the article contains good and important research approaches and first interesting results, but the scientific reporting should be significantly improved.
(If you wish, you can find more detailed comments in the annotated PDF.)

ok.

### 2025-05-23 01-intro.Rmd
edits

Integrating artificial intelligence (AI) into educational settings has been debated for over three decades [@roll2016evolution]. Recent advances in generative AI and large language model (LLM) chatbots have opened even more possibilities for improvements in educational practices [@yan2024promises; @kasneci2023chatgpt; @tlili2023if]. Although LLMs mimic human intelligence, their applications extend beyond imitation and include a range of educational tasks: facilitating problem-solving [@urban2024chatgpt], language learning [@derakhshan2024chatgpt; @song2023enhancing], or evaluation of students' work [@henkel2024can]. However, the impact of these applications on students' learning remains controversial, with proponents highlighting potential benefits and critics cautioning about risks and drawbacks. This study addresses two critical aspects of AI integration in education: the effectiveness of AI-generated explanations and the optimal modes of interaction between AI and students, specifically whether Socratic or alternative approaches yield better outcomes.

A key advancement over previous AI systems is that LLMs can generate step-by-step solutions to accompany their responses to students' queries. This study investigates how LLMs' ability to generate step-by-step explanations influences students' problem-solving skills and their critical evaluation of AI-generated responses. Specifically, we examine the impact of  AI explanations on students' performance in a numerical estimation task and their assessment of the accuracy of AI-generated predictions. Previous research has shown that explanations can foster children’s causal learning and contribute to the development of their scientific reasoning [@dejong1986explanation;@legare2014contributions; @danovitch2021mind]. Similarly,  explanations generated by LLMs may guide students in their problem-solving, for example, by decomposing a numerical estimation task into more manageable steps, such as considering heuristics or approximations. However, LLMs can also generate inaccuracies and flawed reasoning [@saxton2019analysing; @kalyan2021how; @hendrycks2021measuring], misleading students if followed without scrutiny. Understanding this dual role of AI explanations as a valuable educational tool and a potential source of misinformation leads to our first research question (RQ):

@@

The study also aims to explore how different modes of student-AI interaction more broadly influence students' performance and perceptions, of which providing explanations is one key element. Specifically, we contrast two fundamental approaches: the "Socratic” and “non-Socratic” methods. The Socratic approach, inspired by the Socratic teaching method [@lam2011socratic; @dalim2022promoting], engages students through an argumentative dialogue where the AI tutor asks thought-provoking questions to stimulate critical thinking and self-reflection [@wilberding2021socratic]. This method encourages students to think critically and arrive at their answers rather than relying on the AI-generated solution, thus helping students gain more confidence in their reasoning [@cleveland2015beyond]. In contrast, the non-Socratic approach directly answers students' queries without necessarily engaging them in a dialogue or exploration.

@@

The ethical and societal implications of LLMs in education are also complex. Issues such as bias, privacy, surveillance, and autonomy persist, especially in K-12 contexts, where the impact of algorithmic decisions on young learners' agency and privacy can be profound [@williams2024ethical]. LLMs introduce unique challenges, notably in alignment, where the system's goals may not align fully with educational objectives, despite companies' efforts to mitigate such risks through fine-tuning and reinforcement learning [@gabriel2020artificial]. Concerns also extend to students' digital well-being, as AI in education could inadvertently contribute to unhealthy digital habits and reliance on AI assistance over critical thinking [@weidinger2022taxonomy]. Given these multidimensional impacts, further research is needed to optimise AI's role in education, balancing short-term learning gains with long-term skill development and ethical considerations.

@@

Results of our investigation also contribute to the current debate on the pedagogical principles for designing AI-driven systems and educational opportunities, the so-called _design for learning_ [@gavsevic2023empowering]. It underscores the importance of using a multi-disciplinary approach that combines traditional pedagogical insights with principles from human-computer interactions. Consequently, our work adds to the growing efforts to tackle critical challenges in integrating AI into education, helping to automate and scale up tasks like providing feedback, grading, and making learning recommendations [@dai2023can; @yan2024practical; @joksimovic2023opportunities].

>>>>

Integrating artificial intelligence (AI) into educational settings has been debated for over three decades [@roll2016evolution]. Recent advances in generative AI and large language model (LLM) chatbots have opened even more possibilities for improvements in educational practices [@yan2024promises; @kasneci2023chatgpt; @tlili2023if]. Although LLMs mimic human intelligence, their applications extend beyond imitation and include a range of educational tasks: facilitating problem-solving [@urban2024chatgpt], language learning [@derakhshan2024chatgpt; @song2023enhancing], or evaluation of students' work [@henkel2024can]. However, the impact of these applications on students' learning remains controversial, with proponents highlighting potential benefits and critics cautioning about risks and drawbacks [REFs]. This study addresses two critical aspects of AI integration in education: the effectiveness of AI-generated explanations and the optimal modes of interaction between AI and students, specifically whether Socratic or alternative approaches yield better outcomes.

A key advancement over previous AI systems is that LLMs can generate step-by-step solutions to accompany their responses to students' queries. This study investigates how this ability influences students' interactions and helps them enhance their problem-solving skills. Specifically, we first examine the impact of AI explanations on students' performance in a numerical estimation task. We then test whether providing such AI explanations influence students' assessment of the accuracy of AI-generated predictions, compared to presenting the predictions alone. Finally, we test two approaches throught which students can interact with AI chatbots and receive explanations: one approach that encourages critical thinking through incremental guidance ("Socratic AI")  and another providing immediate solutions ("non-Socratic AI").

<!-- A key advancement over previous AI systems is that LLMs can generate step-by-step solutions to accompany their responses to students' queries. This study investigates how LLMs' ability to generate step-by-step explanations influences students' problem-solving skills and their critical evaluation of AI-generated responses. Specifically, we examine the impact of AI explanations on students' performance in a numerical estimation task and their assessment of the accuracy of AI-generated predictions. -->

Previous research has shown that explanations can foster children's causal learning and contribute to the development of their scientific reasoning [@dejong1986explanation;@legare2014contributions; @danovitch2021mind]. Similarly,  explanations generated by LLMs may guide students in their problem-solving, for example, by decomposing a numerical estimation task into more manageable steps, such as considering heuristics or approximations. However, LLMs can also generate inaccuracies and flawed reasoning [@saxton2019analysing; @kalyan2021how; @hendrycks2021measuring], misleading students if followed without scrutiny. Understanding this dual role of AI explanations as a valuable educational tool and a potential source of misinformation leads to our first research question (RQ):

@@

The study also aims to explore how different modes of student-AI interaction more broadly influence students' performance and perceptions. Specifically, we contrast two fundamental approaches: the "Socratic” and “non-Socratic” methods. The Socratic approach, inspired by the Socratic teaching method [@lam2011socratic; @dalim2022promoting], engages students through an argumentative dialogue where the AI tutor asks thought-provoking questions to stimulate critical thinking and self-reflection [@wilberding2021socratic]. This method encourages students to think critically and arrive at their answers rather than relying on the AI-generated solution, thus helping students gain more confidence in their reasoning [@cleveland2015beyond]. In contrast, the non-Socratic approach directly answers students' queries without necessarily engaging them in a dialogue or exploration.

@@

<!-- The ethical and societal implications of LLMs in education are also complex. Issues such as bias, privacy, surveillance, and autonomy persist, especially in K-12 contexts, where the impact of algorithmic decisions on young learners' agency and privacy can be profound [@williams2024ethical]. LLMs introduce unique challenges, notably in alignment, where the system's goals may not align fully with educational objectives, despite companies' efforts to mitigate such risks through fine-tuning and reinforcement learning [@gabriel2020artificial]. Concerns also extend to students' digital well-being, as AI in education could inadvertently contribute to unhealthy digital habits and reliance on AI assistance over critical thinking [@weidinger2022taxonomy]. Given these multidimensional impacts, further research is needed to optimise AI's role in education, balancing short-term learning gains with long-term skill development and ethical considerations. -->

@@

Results of our investigation also contribute to the current debate on the pedagogical principles for designing AI-driven systems and educational opportunities, the so-called _design for learning_ [@gavsevic2023empowering]. It underscores the importance of using a multi-disciplinary approach that combines traditional pedagogical insights with principles from human-computer interactions. Building on recent efforts to address critical challenges in integrating AI into education ---like providing feedback, grading, and making learning recommendations [@dai2023can; @yan2024practical; @joksimovic2023opportunities]--- this study offers insights on how k-12 students engage with alternative forms of AI interaction. In particular, it emphasizes the challenges of embedding classical pedagogical principles, such as the Socratic Method, and the value of providing AI explanations for students compared to just solutions.

### 2025-05-23 02-methods.Rmd
edits

@@

- **User authentication**: A secure and anonymous login system for students.
- **Web Survey**: A web interface to survey students and where they could perform simple tasks online, such as writing a short essay or performing basic calculations.
- **AI Chatbot**: A chatbot powered by GPT-4 provided students with personalised assistance and tutoring during the session. A new chatbot instance was associated with each question for each student, isolating each conversation from interactions in previous questions. The chatbot was available to students only for specific questions or tasks under the researchers' control.
- **Data logging**: A SQL database storing students' conversation logs with the AI chatbot, including texts, timestamps, and survey responses. 
- **Randomised assignment**: A system to randomly assign registered students to different versions of the AI chatbot or treatment groups to explore the causal impact of various configurations on students' interactions and performance.

@@

Recruiting students was conducted after receiving ethical approval from the European Commission's internal Ethical Review Board, ensuring that the consent procedures, data protection requirements, and the experimental protocol complied with local laws and were safe for the participants. The data privacy protection protocol was approved by the Commission's data protection officer. As an additional safeguard, given the minor age of the participants, we required their parents or legal guardians to provide us with written consent, allowing their children to participate in the study. The students also had to give their assent to participate by completing an online consent form.

@@

About ten experimental sessions were conducted at the schools between November 11 and 12, 2023, in Brussels and February 8 and 9, 2024, in Seville. Each session took about two hours. In the first 45-60 minutes, students received a personal computer and were asked to perform multiple tasks online using the AI tutor, including answering a questionnaire. In the following 45-60, there was a group discussion on how the students found the interactions with the AI tutor and a more general debate on how they perceived the potential benefits and drawbacks of integrating LLMs in the classroom. The results of the group discussions are not discussed in this paper; however, they were used as material for interpreting the results of the experimental study.

@@

Figure \@ref(fig:design) illustrates the two randomised manipulations in our experimental design: (1) AI step-by-step reasoning and (2) Socratic vs non-Socratic AI.

@@

The first manipulation focuses on a task in which students are asked to estimate the value of coins in a jar (see Section \@ref(sec:si-ai-explanation) for the details).[^jar] Specifically, we used the coin jar from Steiner's experiment [@steiner2015turns], aimed originally at assessing Internet users' guessing accuracy. For this intervention, we varied the AI’s response by providing either a complete answer, which included both an estimated value and a step-by-step explanation generated by the AI tutor, or a partial answer that provided only the estimate without additional details. In both conditions, all participants received the same estimated value ($213), but those in the full-answer condition also viewed an explanation outlining the step-by-step reasoning the AI used to arrive at this estimation based on the jar image.[^jar-gpt4]

@@

```{r prompts}
df_prompts <- data.frame(
  "AI Tutor" = c("Socratic", "Non-Socratic"),
  "Prompt instruction" = c("You are a Socratic tutor. You always answer using the Socratic style, asking just the right questions to help students learn to think for themselves, breaking down the problem into simpler parts until it's at the right level for them. You provide concise information and explanations understandable for 8th to 10th grade students.", "You are a didactic tutor. You provide concise information and explanations understandable for 8th to 10th grade students.")
)
kbl(df_prompts, booktabs = TRUE, caption = "Prompt instructions associated with the AI Tutor's treatments") |>
  kableExtra::column_spec(2, "4in")
```

>>>>

We conducted a field experiment across two schools to investigate the impact of different AI tutoring strategies on students' critical thinking, self-confidence, and task performance. Participants engaged with a custom-designed web application, the _AI Tutor_, which randomly assigned students to interact with distinct versions of GPT-4-based chatbots during structured educational activities. The experimental design featured two primary manipulations: (1) the presence of step-by-step reasoning by the AI and (2) the use of Socratic versus non-Socratic dialogue styles. To assess the effects, we employed objective performance measures alongside pre- and post-task surveys capturing students' cognitive and affective responses. The following subsections detail the AI Tutor system, participant characteristics, and experimental procedures.

@@

- **User authentication**: A secure and anonymous login system for students.
- **Web Survey**: A web interface to collect data from students, including answering survey questions and perform simple tasks, such as writing a short essay or solving simple math problems.
- **AI Chatbot**: A chatbot powered by GPT-4 provided students with personalised assistance and tutoring during the session. A new chatbot instance was associated with each question for each student, isolating each conversation from interactions in previous questions. The chatbot was available to students only for specific questions or tasks under the researchers' control.
- **Data logging**: A SQL database storing students' conversation logs with the AI chatbot, including texts, timestamps, and survey responses. 
- **Randomised assignment**: A system to randomly assign registered students to different versions of the AI chatbot or treatment groups to explore the causal impact of various configurations on students' interactions and performance.

@@

Recruiting students was conducted after receiving ethical approval from the European Commission's internal Ethical Review Board, ensuring that the consent procedures, data protection requirements, and the experimental protocol complied with local laws and ethical research standards. The data privacy protection protocol was approved by the Commission's data protection officer. As an additional safeguard, given the minor age of the participants, we required their parents or legal guardians to provide us with written consent, allowing their children to participate in the study. The students also had to give their assent to participate by completing an online consent form.

@@

About ten experimental sessions were conducted at the schools between November 11 and 12, 2023, in Brussels and February 8 and 9, 2024, in Seville. Each session took about two hours. In the first 45-60 minutes, students received a personal computer and were asked to perform three main tasks using the AI tutor and answer a questionnaire without the AI tutor. In the following 45-60, there was a group discussion on how the students judged the interactions with the AI tutor and a more general debate on how they perceived the potential benefits and drawbacks of integrating LLMs in the classroom. The results of the group discussions are not discussed in this paper; however, they were used as material for interpreting the results of the experimental study.

@@

Figure \@ref(fig:design) illustrates the two  randomised manipulations in our experimental design: (1) AI step-by-step reasoning and (2) Socratic vs non-Socratic AI. It is important to note that these were conducted as independent experiments, with different dependent and independent variables, rather than a factorial 2x2 design.

@@

The first manipulation focuses on a task in which students are asked to estimate the value of coins in a jar (see Section \@ref(sec:si-ai-explanation) for the details).[^jar] Specifically, we used the coin jar from Steiner's experiment [@steiner2015turns], aimed originally at assessing Internet users' guessing accuracy. For this intervention, we varied the AI's response by providing either a complete answer, which included both an estimated value and a step-by-step explanation generated by the AI tutor, or a partial answer that provided only the estimate without additional details. In both conditions, all participants received the same estimated value ($213), but those in the full-answer condition also viewed an explanation outlining the step-by-step reasoning the AI used to arrive at this estimation based on the jar image.[^jar-gpt4]

@@

```{r prompts}
df_prompts <- data.frame(
  "AI Tutor" = c("Socratic", "Non-Socratic"),
  "Prompt instruction" = c("You are a Socratic tutor. You always answer using the Socratic style, asking just the right questions to help students learn to think for themselves, breaking down the problem into simpler parts until it's at the right level for them. You provide concise information and explanations understandable for 8th to 10th grade students.", "You are a didactic tutor. You provide concise information and explanations understandable for 8th to 10th grade students.") # nolint
)
kbl(
  df_prompts, booktabs = TRUE,
  caption = "Prompt instructions associated with the AI Tutor's treatments"
) |>
  kableExtra::column_spec(2, "4in")
```

### 2025-05-23 03-results.Rmd
edits

```{r summary-statistics, echo = FALSE, warning=FALSE, message=FALSE}
tutorgpt %>%
  dplyr::select(
    treatment_tutor_id,
    "Gender" = gender,
    "Has used ChatGPT" = has_used_before,
    "Location" = location,
    "Grades" = top_grades,
    "Homework weekly study" = hours_per_week,
    "Homework on time" = on_time_completion,
    "Homework difficulties" = factors_contributing,
    "Self-efficacy (sound)" = q5_self_physics,
    "Self-efficacy (essay)" = q6_self_technology,
    "Self-efficacy (guess)" = q7_self_swimming_pool,
  ) %>%
  tidyr::pivot_longer(-treatment_tutor_id) %>%
  dplyr::count(name, value, treatment_tutor_id) %>%
  na.omit() %>%
  dplyr::mutate(percent = 100 * n / sum(n), 
                .by = c(name, treatment_tutor_id)) %>%
  tidyr::pivot_wider(names_from = treatment_tutor_id,
                     values_from = c(percent, n),
                     values_fill = 0) %>%
  dplyr::mutate(name = ifelse(row_number() == 1, name, ""), .by = name) %>% 
  dplyr::mutate(totals = n_non_socratic + n_socratic) %>%
  dplyr::select(
    "Name" = name,
    "Value" = value,
    "% Non-Socratic" = percent_non_socratic,
    "% Socratic" = percent_socratic,
    "N" = totals
  ) %>% 
  kableExtra::kbl(
    digits = 1,
    caption = "Sample characteristics",
    booktabs = TRUE,
    linesep = if (knitr::is_latex_output()) "\\hline" else ""
  ) %>% 
  kableExtra::kable_styling()
```

>>>>

```{r summary-statistics, echo = FALSE, warning=FALSE, message=FALSE}
tutorgpt_rename <- tutorgpt %>%
  dplyr::select(
    treatment_tutor_id, 
    treatment_explain_id,
    "Gender" = gender,
    "Has used ChatGPT" = has_used_before,
    "Location" = location,
    "Grades" = top_grades,
    "Homework weekly study" = hours_per_week,
    "Homework on time" = on_time_completion,
    "Homework difficulties" = factors_contributing,
    "Self-efficacy (sound)" = q5_self_physics,
    "Self-efficacy (essay)" = q6_self_technology,
    "Self-efficacy (guess)" = q7_self_swimming_pool,
  )

table_socratic <- tutorgpt_rename %>%
  select(-treatment_explain_id) %>% 
  tidyr::pivot_longer(-treatment_tutor_id) %>%
  mutate(pval = xtabs(~ value + treatment_tutor_id) %>% 
                fisher.test() %>% 
                .$p.value,
        .by = name)  %>% 
  dplyr::count(name, value, pval, treatment_tutor_id) %>%
  na.omit() %>%
  dplyr::mutate(percent = 100 * n / sum(n), 
                .by = c(name, treatment_tutor_id)) %>%
  tidyr::pivot_wider(names_from = treatment_tutor_id,
                     values_from = c(percent, n),
                     values_fill = 0) %>%
  dplyr::mutate(totals = n_non_socratic + n_socratic)

table_explain <- tutorgpt_rename %>%
  select(-treatment_tutor_id) %>% 
  tidyr::pivot_longer(-treatment_explain_id) %>%
  dplyr::mutate(pval_explain = xtabs(~ value + treatment_explain_id) %>% 
                               fisher.test() %>% 
                                .$p.value, 
                .by = name)  %>% 
  dplyr::count(name, value, treatment_explain_id, pval_explain) %>%
  na.omit() %>%
  dplyr::mutate(percent = 100 * n / sum(n), 
                .by = c(name, treatment_explain_id)) %>%
  tidyr::pivot_wider(names_from = treatment_explain_id,
                     values_from = c(percent, n),
                     values_fill = 0)

table_socratic %>% 
  left_join(table_explain, by = c("name", "value")) %>% 
  mutate(name = ifelse(row_number() == 1, name, ""), 
         pval = ifelse(row_number() == 1, sprintf("%0.2f", pval), ""),
         pval_explain = ifelse(row_number() == 1, sprintf("%0.2f", pval_explain), ""),
         .by = name) %>%
  dplyr::select(
      name, value,
      percent_socratic, percent_non_socratic, pval,
      percent_explain_yes, percent_explain_no, pval_explain,
      totals,
  ) %>% 
  kableExtra::kbl(
    col.names = c(
      "Name", "Value",
      "Yes", "No", "p.",
      "Yes", "No", "p.",
      "N"
    ),
    digits = 0,
    booktabs = TRUE,
    caption = "Sample Characteristics",
    linesep = if (knitr::is_latex_output()) "\\hline" else "",
  ) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::add_header_above(c(" " = 2, "Socratic (%)" = 3,
                                 "AI Explain (%)" = 3, " "))
```

### 2025-05-23 main_report.Rmd
edits

toc: false
fontsize: 11pt # 11
linestretch: 2 # 1.25
colorlinks: true
link-citations: true
graphics: true
tables: true
mainfont: Times New Roman
geometry: margin=2cm
bibliography: bibliography/refs.bib
always_allow_html: true

>>>>

toc: false
fontsize: 11pt # 11
linestretch: 2 # 1.25
colorlinks: true
link-citations: true
graphics: true
tables: true
mainfont: Times New Roman
geometry: margin=2cm
bibliography: [References/refs.bib]
always_allow_html: true
